Phylogenetics and the human microbiome.

### 2014-06-24 sbreview.tex
Typo fix.

There are many OTU inference methods with various speeds and strategies.
Some methods proceed through a list of sequences and progressively add each either to an existing cluster or start a new cluster with that sequence, such as CD-HIT \citep{li2006cdhit} and USEARCH \citep{edgar2010usearch}, while UPARSE \citep{edgar2013uparse} uses a similar strategy while also attempting to correct for sequencing error.
\citet{white2010alignment} show that different ways of doing this genre of heuristic clustering can result in very different results.
\citet{Cai2011-bi} perform highly efficient clustering using a pseudometric based partition tree, which can be thought of as a hierarchical clustering tree with a fixed set of internal node heights.
\citet{navlakha2009finding} take a semi-supervised approach in that input includes sequences along with a subset of sequences that are equipped with taxonomic classifications; the algorithm then groups all sequences (many in novel clusters) into clusters that have similar properties as the example taxonomic clusters.
\citet{Wang2013-ol} optimize a criterion of cluster modularity.
\citet{hao2011clustering} use a Gaussian mixture model formulation for clustering to avoid fixed cutoff values, and \citet{CWC12} use a two step process, first with a Dirichlet multinomial mixture on 4-mer profiles, and then a minimum description length criterion.
\citet{Zhang2013-wh} have developed a phylogenetic means to do species delimitation that scales to a relatively large number of sequencing reads and so can be used as an OTU clustering method.

>>>>

There are many OTU inference methods with various speeds and strategies.
Some methods proceed through a list of sequences and progressively add each either to an existing cluster or start a new cluster with that sequence, such as CD-HIT \citep{li2006cdhit} and USEARCH \citep{edgar2010usearch}, while UPARSE \citep{edgar2013uparse} uses a similar strategy while also attempting to correct for sequencing error.
\citet{white2010alignment} show that different ways of doing this genre of heuristic clustering can result in very different results.
\citet{Cai2011-bi} perform highly efficient clustering using a pseudometric based partition tree, which can be thought of as a hierarchical clustering tree with a fixed set of internal node heights.
\citet{navlakha2009finding} take a semi-supervised approach in that input includes sequences along with a subset of sequences that are equipped with taxonomic classifications; the algorithm then groups all sequences (many in novel clusters) into clusters that have similar properties as the example taxonomic clusters.
\citet{Wang2013-ol} optimize a criterion of cluster modularity.
\citet{hao2011clustering} use a Gaussian mixture model formulation for clustering to avoid fixed cutoff values, and \citet{CWC12} use a two step process, first with a Dirichlet multinomial mixture on 3-mer profiles, and then a minimum description length criterion.
\citet{Zhang2013-wh} have developed a phylogenetic means to do species delimitation that scales to a relatively large number of sequencing reads and so can be used as an OTU clustering method.
